Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame

### 2022-05-18 manuscript/Chapter3-manuscript.Rmd
updated the plan
wrote last paragraph of intro

---
title: "How hunting experience and prey predictability jointly shape individual foraging and diet specialisation of a predator within an online multiplayer videogame"
output: 
  word_document:
    reference_docx: Chapter3-styles.docx
bibliography: references.bib
csl: american-naturalist.csl
---

@@

Keywords: individual variation, hunting success, plasticity, learning, prey predictability, online videogames

@@

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources]. A potential consequence of among-individual differences in foraging behavior is that they can lead to individual differences in the type of prey captured (i.e. individual niche specialization) [Woo et al., 2008, sources]. There may thus exist a functional relationship linking individual foraging specialisation to specialisation in resource consumption [sources: Toscano et al. 2016, etc, michalko et gibbons, Kerr, Tinker, Bowen]. This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.]. For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc]. However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual differences. Therefore, we still have limited knowledge on how individual foraging specialisation arises, and its ecological and community consequences.

@@

@@

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive.

@@

- Paragraphe 1 (effet de la taille, du sexe, et importance du foraging mode)

- Paragraphe 2 (importance des proies (woo et al.) et de l'habitat)

- Paragraphe 3 (importance de l'expérience et comment c'est un rôle probable mais encore inexploré) (sources Weimerskirch, 2005, 2007)

@@

>>>>

---
title: "Hunting experience and prey predictability jointly shape individual foraging specialisation in a predator-prey videogame"
output: 
  word_document:
    reference_docx: Chapter3-styles.docx
bibliography: references.bib
csl: american-naturalist.csl
---

@@

Keywords: foraging behaviour, individual specialization, experience, learning, prey predictability, online videogames

@@

Individual variation in predator foraging behaviour is increasingly recognized as a major driver of trophic interactions and community dynamics [sources].
*Ideas* : 
- * usually measured at the population level*
- * we now have metrics that enable the quantification of individual specialization*

A potential consequence of among-individual differences in foraging behavior is that they can lead to individual differences in the type of prey captured (i.e. individual niche specialization) [Woo et al., 2008, sources]. There may thus exist a functional relationship linking individual foraging specialisation to specialisation in resource consumption [sources: Toscano et al. 2016, etc, michalko et gibbons, Kerr, Tinker, Bowen]. This would imply that predators need to develop foraging tactics that are fine tuned to specific prey attributes or prey types [sources: Phillips, Woo, etc.]. *ICI GARDER LES IDÉES MAIS METTRE L'ACCENT SUR LE FAIT QUE C'EST LES PROIES DISPONIBLES AU LIEU DES PROIES MANGÉES*

For instance, predators species often use stereotyped hunting techniques required to capture the type of prey they encounter, such as (dauphins, orcas, etc) [sources : Woo, Estes, tinker, etc]. However, it remains largely unclear how extrinsinc and intrinsinct factors interact to shape these individual differences. Therefore, we still have limited knowledge on how individual foraging specialisation arises, and its ecological and community consequences.

@@

Hunting experience has been proposed as a potential major driver of the relationship between foraging specialisation and resource use [sources]. Learning how to hunt is crucial for young predators to reach adulthood and survive. (check Urszan et al)

@@

@@

- Paragraphe 1 : Importance of among-individual variation in foraging behaviour

- Paragraphe 2 : Factors shaping individual variation in foraging behaviour - the role of experience
  (sources Weimerskirch, 2005, 2007) (explain mechanisms). Explain how it may unravel why foraging specialists are often thought to be more succesful.

- Paragraphe 3: (Linking prey variability to experience (woo et al.)) how trophic interactions are probably the main driver of learning and experience

@@

*Idéé* :
- Est-ce que ça se pourrait que les proies déterminent si les prédateurs se spécialize avec l'expérience ou plutôt deviennent flexible? Dans ce cas, j'utiliserais pas la covariance mais le comportement des proies en effet fixe sur la variance? ou il faudrait que je change les covariances?

# Dernier paragraphe intro (Thèsez-vous)
Here, we collected individual behavioural data from players in *Dead by Daylight* to investigate how hunting experience and the behavioural variation in prey encountered shaped predator foraging specialization. This enabled us to have a high degree of precision on the interaction as both the behaviour of the predator and the four prey were measured simultaneously in each trial. First, we hypothesize that individual hunting behaviour will change with hunting experience. If experience reduces the costs of switching tactics, then predators should become more flexible through time. Alternatively, if experience enables the refinement of the hunting tactics, then individuals may instead specialize through time. Second, we hypothesize that prey behaviour will shape the developmental trajectories of the predator foraging behaviour. Whether predators specialize or not with experience may depend on the behaviour of their prey, for instance, as it may be harder to specialize on prey that are more variable. Third, if individuals differ in their degree of foraging specialization, then we expect that the success of foraging specialists and generalists will be equal. Specialist hunters should fare better when prey variability is lower, while flexible hunters will fare better when prey variability is higher.
